Slavnov products and KP tau functions

### 2025-04-11 draft.tex
add more details on tau functions

We can show, see~\cite{Araujo:2021ghu} for a detailed proof of this
statement, that the tau function~\ref{eq:tau-function} admits an
integral representation of the form (ignoring the signs dependence on
the length \(n\) of the spin chain)
\todo{\tiny I need to do this calculation carefully now. The contour that gives the
  representation below should avoid the Bethe root \(v_k\), otherwise, we pick
poles we want to avoid.}
\begin{equation}
  \label{eq:tau-function-miwa}
  \bm{\tau}(\bm{t}, \bm{v}) = 
    \det_{j,k}\left(
    \oint \frac{d w}{2\pi i} e^{\bm{\xi}(\bm{t}, w^{-1})} \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k} \; ,
    \right)
\end{equation}
where 
\begin{equation}
  \bm{\xi}(\bm{t}, w^{-1}) = \sum_{p=1}^\infty t_p w^{-p}\; .
\end{equation}
One of the advantages of this representation is that now it makes
sense to consider the limit of the infinite chain, \(n\to \infty\).

>>>>

It is easy to show that that the tau function~(\ref{eq:tau-function})
admits an integral representation of the form
\begin{equation}
  \label{eq:tau-function-miwa}
  \bm{\tau}(\bm{t}, \bm{v}) = 
    \det_{j,k}\left(
    \oint_{\gamma_k} \frac{d w}{2\pi i} e^{\bm{\xi}(\bm{t}, w^{-1})} \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k} \; ,
    \right)
\end{equation}
where 
\begin{equation}
  \bm{\xi}(\bm{t}, w^{-1}) = \sum_{p=1}^\infty t_p w^{-p}\; ,
\end{equation}
and the integration contour \(\gamma_k\) encloses all points
\(\{z_j\}_{j=1}^n\) but avoids the Bethe root \(v_k\).  For a detailed
proof of this statement, one may check the
reference~\cite{Araujo:2021ghu}.  The only difference now is that now
we need to be carefull with the integration contour \(\gamma_k\).

One of the advantages of this representation is that now it makes
sense to consider the limit of the infinite chain, \(n\to \infty\).
